\begin{thebibliography}{9} 

\bibitem{Kaggle} 
Kaggle. \textit{Second Annual Data Science Bowl,}
\\\texttt{\url{https://www.kaggle.com/c/second-annual-data-science-bowl}}

\bibitem{Michael_Nielsen} 
Michael Nielsen. \textit{Neural Networks and Deep Learning,}
\\\texttt{\url{http://neuralnetworksanddeeplearning.com}}

\bibitem{Deep_Learning} 
Ian Goodfellow and Yoshua Bengio and Aaron Courville. \textit{Deep Learning,}
\\\texttt{\url{http://www.deeplearningbook.org}}

\bibitem{Convolutional}
Fei-Fei Li, Justin Johnson, Serena Yeung. \textit{Convolutional Neural Networks for Visual Recognition,}
\\\texttt{\url{http://cs231n.github.io}}

\bibitem{DICOM} 
\textit{DICOM Tutorial,}
\\\texttt{\url{https://www.neologica.it/html/tutorial/TutorialDICOM}}

\bibitem{ADAM} 
Diederik P. Kingma, Jimmy Lei Ba. \textit{ADAM: A Method for stochastic optimization,}
\\\texttt{\url{https://arxiv.org/pdf/1412.6980.pdf}}

\bibitem{Karen_Simonyan} 
Karen Simonyan, Andrew Zisserman. \textit{Very deep convolitional networks for large-scale image recognition,}
\\\texttt{\url{https://arxiv.org/pdf/1409.1556.pdf}}

\bibitem{Gradient_Boosting} 
Jerome H. Friedman. \textit{Greedy Function Approximation: A Gradient Boosting Machine,}
\\\texttt{\url{https://statweb.stanford.edu/~jhf/ftp/trebst.pdf}}

\bibitem{CLAHE} 
Sujin Philip. \textit{Contrast Limited Adaptive Histogram Equalization,}
\\\texttt{\url{http://file.scirp.org/pdf/ENG_2013110109155688.pdf}}

\bibitem{Cardiovascular} 
Carmen Bunu. \textit{Sistemul Cardiovascular,}
\\\texttt{\url{http://fiziologie.umft.ro/ro/CV5.PDF}}

\bibitem{Krizhevsky} 
Alex Krizhevsky. \textit{Learning Multiple Layers of Features from Tiny Images,}
\\\texttt{\url{https://www.cs.toronto.edu/~kriz/learning-features-2009-TR.pdf}}

\bibitem{Yoshua_Bengio} 
Yoshua Bengio. \textit{Learning Deep Architectures for AI,}
\\\texttt{\url{http://www.iro.umontreal.ca/~bengioy/papers/ftml_book.pdf}}

\bibitem{Vinod_Nair} 
Vinod Nair, Geoffrey E. Hinton. \textit{Rectified Linear Units Improve Restricted Boltzmann Machines,}
\\\texttt{\url{http://www.cs.toronto.edu/~fritz/absps/reluICML.pdf}}

\bibitem{Simon_Prince} 
Simon J.D. Prince. \textit{Computer vision: models, learning and inference.}

\bibitem{Richard_Szeliski} 
Richard Szeliski. \textit{Computer Vision: Algorithms and Applications.}

\end{thebibliography}